DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2019-02-25 rebuttal.tex

\subsection{}

\begin{mdframed}[style=comment]
I have read with great interest the paper by Perraudin and collaborators presenting a methodology (and the associated code) for performing deep machine learning on the sphere using novel algorithms.

The paper is well-written, and the results are clearly presented. The litterature as well as the advantages and limitations of new and existing algorithms are discussed thoroughly and fairly. I recommend this paper for publication, provided the following comments are addressed.
\end{mdframed}

Dear reviewer, we thank you for your time and thorough comments. The manuscript improved thanks to your feedback. You can find a detailed answer to all the points you mentioned in this rebuttal.

@@

We agree that the ML algorithms should be tested on the same input data for a fair comparison.
%In practice, those models are limited by the computational power and the dataset size.

We did try to train an SVM on the raw data but were unable to obtain over $60\%$ accuracy in the three noiseless cases, which is far behind every other tested model.
Practically, the classifier would either overfit or be over-regularized.
We hence decided not to report the raw-data SVM results in the paper.
This information has now been added to the manuscript.
% \nati{FYI, I did try again to be entirely sure about it.}

### 2019-02-25 scnn.tex
comment 1.2

It may seem unfair to compare DeepSphere, who has access to raw pixels, with SVMs who only see limited features (histograms and PSDs).
We however trained an SVM on the raw pixels and were unable to obtain over $60\%$ accuracy in the easiest cases (i.e., noiseless).
(Remember that every other tested model is close to $100\%$ in that setting.)
% TODO: provide an explanation why?

>>>>

It may seem unfair to compare DeepSphere, who has access to raw pixels, with SVMs who only see limited features (histograms and PSDs).
We however trained an SVM on the raw pixels and were unable to obtain over $60\%$ accuracy in any of the three noiseless cases.
